---
title: "DS301FinalProject"
author: "Jack Novak"
date: "5/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(glmnet)
library(readr)
library(MASS)
library(class)
library(leaps)
library(dplyr)
library(car)
library(cvms)
library(tibble)
options(warn = -1)
```

#credit Caroly Coronado-Vargas
```{r}
salary1 <- read.csv(file ='ds_salary_data.csv')
region_key <- data.frame(state.abb, state.region)
salary1$state.abb <- as.factor(salary1$Job.Location)
salary<- merge(salary1,region_key, by = "state.abb")
salary<- salary[,-c(1,2,4,7,9,11,12)] 
salary$Size <- as.factor(salary$Size)
salary$Type.of.ownership<- as.factor(salary$Type.of.ownership)
salary$Sector <- as.factor(salary$Sector)
salary$Hourly <- as.factor(salary$Hourly)
salary$Python <- as.factor(salary$Python)
salary$excel <- as.factor(salary$excel)
salary$sql <- as.factor(salary$sql)
salary$sas <- as.factor(salary$sas)
salary$tableau <- as.factor(salary$tableau)
salary$job_title_sim <- as.factor(salary$job_title_sim)
salary$Degree <- as.factor(salary$Degree)
trimed = salary[!(salary$Degree == "na"),]
```


# John's Portion
### Basic first models

```{r}
#basic logistic regression with all listed degree levels including na
model2 <- glm(Degree ~ Avg.Salary.K.+Python+excel+sql+sas+aws+tableau, data = salary, family = binomial)
summary(model2)
#basic logistic regression with all listed degree levels including na
model4 <- glm(job_title_sim ~ Avg.Salary.K.+Python+excel+sql+sas+aws+tableau+Degree, data = salary, family = binomial)
summary(model4)
```

### data classification
```{r}
set.seed(7)
salary$job_title_sim <- as.numeric(salary$job_title_sim)
salary$Degree <- as.numeric(salary$Degree)
salary$state.region <- as.numeric(salary$state.region)
splt<- sample(c(rep(0, 0.7 * nrow(salary)), rep(1, 0.3 * nrow(salary))))
train <- salary[splt == 0, ]
test <- salary[splt == 1, ] 
```

  classify expected job using all other variables
```{r}
model5 <- glm(job_title_sim ~., data = train)
predictions <- predict(model5, newdata = test)
predictions <- round(predictions, digits = 0)
d_multi <- tibble("target" = test$job_title_sim ,"prediction" = predictions)
conf_mat1 <- confusion_matrix(targets = d_multi$target, predictions = d_multi$prediction)
plot_confusion_matrix(conf_mat1$`Confusion Matrix`[[1]])
```

  classify expected education using all other variables
```{r}
model6 <- glm(Degree ~., data = train)
predictions <- predict(model6, newdata = test)
predictions <- round(predictions, digits = 0)
d_multi <- tibble("target" = test$Degree ,"prediction" = predictions)
conf_mat1 <- confusion_matrix(targets = d_multi$target, predictions = d_multi$prediction)
plot_confusion_matrix(conf_mat1$`Confusion Matrix`[[1]])
```

  classify expected location using all other variables
```{r}
model7 <- glm(state.region ~., data = train)
predictions <- predict(model7, newdata = test)
predictions <- round(predictions, digits = 0)
predictions <- ifelse(predictions == 5, 4, predictions)
d_multi <- tibble("target" = test$state.region ,"prediction" = predictions)
conf_mat1 <- confusion_matrix(targets = d_multi$target, predictions = d_multi$prediction)
plot_confusion_matrix(conf_mat1$`Confusion Matrix`[[1]])
```

  lastly classifying if some jobs require specific degrees
```{r}
model8 <- glm(job_title_sim ~ Degree, data = train)
predictions <- predict(model8, newdata = test)
predictions <- round(predictions, digits = 0)
d_multi <- tibble("target" = test$job_title_sim ,"prediction" = predictions)
conf_mat1 <- confusion_matrix(targets = d_multi$target, predictions = d_multi$prediction)

plot_confusion_matrix(conf_mat1$`Confusion Matrix`[[1]])
# Trimmed Na values from the degree to see if it was skewing the outcome
trimed$job_title_sim <- as.numeric(trimed$job_title_sim)
trimed$Degree <- as.numeric(trimed$Degree)
trimed$state.region <- as.numeric(trimed$state.region)
splt<- sample(c(rep(0, 0.7 * nrow(trimed)), rep(1, 0.3 * nrow(trimed))))
train <- salary[splt == 0, ]
test <- salary[splt == 1, ] 
model9 <- glm(job_title_sim ~ Degree, data = train)
predictions <- predict(model9, newdata = test)
predictions <- round(predictions, digits = 0)
d_multi <- tibble("target" = test$job_title_sim ,"prediction" = predictions)
conf_mat1 <- confusion_matrix(targets = d_multi$target, predictions = d_multi$prediction)
plot_confusion_matrix(conf_mat1$`Confusion Matrix`[[1]])
```

  To conclude Degree appears to be an impactful predictor to job title, but does not see to be as large as important as other factors in the data set.
  
# KNN by Jack
  
```{r}
n<-nrow(salary)
salary<-salary%>%
  dplyr::select(Rating, Avg.Salary.K., Age, Degree)

standardized.X = scale(salary)

#80-20 split
test = sample(1:n, 0.2*n)

train.X = standardized.X[-test,-4]
test.X = standardized.X[test,-4]
train.Y = salary$Degree[-test]
test.Y = salary$Degree[test]

#k = 1
knn.pred = knn(train.X,test.X,train.Y,k=1)
head(knn.pred)

table(knn.pred,test.Y)
mean(test.Y!=knn.pred)
```
  
```{r}
k=3
knn.pred = knn(train.X,test.X,train.Y,k=3)
head(knn.pred)

table(knn.pred,test.Y)
mean(test.Y!=knn.pred)
```
  
```{r}
# k=5
knn.pred = knn(train.X,test.X,train.Y,k=1)
head(knn.pred)

table(knn.pred,test.Y)
mean(test.Y!=knn.pred)
```
  
```{r}
# k = 7
knn.pred = knn(train.X,test.X,train.Y,k=7)
head(knn.pred)

table(knn.pred,test.Y)
mean(test.Y!=knn.pred)
```
  
```{r}
# k = 9
knn.pred = knn(train.X,test.X,train.Y,k=9)
head(knn.pred)

table(knn.pred,test.Y)
mean(test.Y!=knn.pred)
```
  
  