```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(glmnet)
library(MASS)
library(caret)
library(class)
library(leaps)
library(dplyr)
library(car)
library(cvms)
library(tibble)
options(warn = -1)
```

#credit Caroly Coronado-Vargas
```{r}
salary1 <- read.csv(file = 'ds_salary_data.csv')
region_key <- data.frame(state.abb, state.region)
salary1$state.abb <- as.factor(salary1$Job.Location)
salary<- merge(salary1,region_key, by = "state.abb")
salary<- salary[,-c(1,2,4,7,9,11,12)] 
salary$Size <- as.factor(salary$Size)
salary$Type.of.ownership<- as.factor(salary$Type.of.ownership)
salary$Sector <- as.factor(salary$Sector)
salary$Hourly <- as.factor(salary$Hourly)
salary$Python <- as.factor(salary$Python)
salary$excel <- as.factor(salary$excel)
salary$sql <- as.factor(salary$sql)
salary$sas <- as.factor(salary$sas)
salary$tableau <- as.factor(salary$tableau)
salary$job_title_sim <- as.factor(salary$job_title_sim)
salary$Degree <- as.factor(salary$Degree)
trimed = salary[!(salary$Degree == "na"),]
```


# John's Portion
### Basic first models

```{r}
#basic logistic regression with all listed degree levels including na
model2 <- glm(Degree ~ Avg.Salary.K.+Python+excel+sql+sas+aws+tableau, data = salary, family = binomial)
summary(model2)
#basic logistic regression with all listed degree levels including na
model4 <- glm(job_title_sim ~ Avg.Salary.K.+Python+excel+sql+sas+aws+tableau+Degree, data = salary, family = binomial)
summary(model4)
```

### data classification
```{r}
set.seed(7)
salary$job_title_sim <- as.numeric(salary$job_title_sim)
salary$Degree <- as.numeric(salary$Degree)
salary$state.region <- as.numeric(salary$state.region)
splt<- sample(c(rep(0, 0.7 * nrow(salary)), rep(1, 0.3 * nrow(salary))))
train <- salary[splt == 0, ]
test <- salary[splt == 1, ] 
```

  classify expected job using all other variables
```{r}
model5 <- glm(job_title_sim ~., data = train)
predictions <- predict(model5, newdata = test)
predictions <- round(predictions, digits = 0)
d_multi <- tibble("target" = test$job_title_sim ,"prediction" = predictions)
conf_mat1 <- confusion_matrix(targets = d_multi$target, predictions = d_multi$prediction)
plot_confusion_matrix(conf_mat1$`Confusion Matrix`[[1]])
```

  classify expected education using all other variables
```{r}
model6 <- glm(Degree ~., data = train)
predictions <- predict(model6, newdata = test)
predictions <- round(predictions, digits = 0)
d_multi <- tibble("target" = test$Degree ,"prediction" = predictions)
conf_mat1 <- confusion_matrix(targets = d_multi$target, predictions = d_multi$prediction)
plot_confusion_matrix(conf_mat1$`Confusion Matrix`[[1]])
```

  classify expected location using all other variables
```{r}
model7 <- glm(state.region ~., data = train)
predictions <- predict(model7, newdata = test)
predictions <- round(predictions, digits = 0)
predictions <- ifelse(predictions == 5, 4, predictions)
d_multi <- tibble("target" = test$state.region ,"prediction" = predictions)
conf_mat1 <- confusion_matrix(targets = d_multi$target, predictions = d_multi$prediction)
plot_confusion_matrix(conf_mat1$`Confusion Matrix`[[1]])
```

  lastly classifying if some jobs require specific degrees
```{r}
model8 <- glm(job_title_sim ~ Degree, data = train)
predictions <- predict(model8, newdata = test)
predictions <- round(predictions, digits = 0)
d_multi <- tibble("target" = test$job_title_sim ,"prediction" = predictions)
conf_mat1 <- confusion_matrix(targets = d_multi$target, predictions = d_multi$prediction)

plot_confusion_matrix(conf_mat1$`Confusion Matrix`[[1]])
# Trimmed Na values from the degree to see if it was skewing the outcome
trimed$job_title_sim <- as.numeric(trimed$job_title_sim)
trimed$Degree <- as.numeric(trimed$Degree)
trimed$state.region <- as.numeric(trimed$state.region)
splt<- sample(c(rep(0, 0.7 * nrow(trimed)), rep(1, 0.3 * nrow(trimed))))
train <- salary[splt == 0, ]
test <- salary[splt == 1, ] 
model9 <- glm(job_title_sim ~ Degree, data = train)
predictions <- predict(model9, newdata = test)
predictions <- round(predictions, digits = 0)
d_multi <- tibble("target" = test$job_title_sim ,"prediction" = predictions)
conf_mat1 <- confusion_matrix(targets = d_multi$target, predictions = d_multi$prediction)
plot_confusion_matrix(conf_mat1$`Confusion Matrix`[[1]])
```

  To conclude Degree appears to be an impactful predictor to job title, but does not see to be as large as important as other factors in the data set.
  
# KNN by Jack
  
```{r}
n<-nrow(salary)
salary<-salary%>%
  dplyr::select(Rating, Avg.Salary.K., Age, Degree)

standardized.X = scale(salary)

#80-20 split
test = sample(1:n, 0.2*n)

train.X = standardized.X[-test,-4]
test.X = standardized.X[test,-4]
train.Y = salary$Degree[-test]
test.Y = salary$Degree[test]

#k = 1
knn.pred = knn(train.X,test.X,train.Y,k=1)
head(knn.pred)

table(knn.pred,test.Y)
mean(test.Y!=knn.pred)
```
  
```{r}
set.seed(1)
n<-nrow(salary)
salary<-salary%>%
  dplyr::select(Rating, Avg.Salary.K., Age, Degree)
standardized.X = (salary)

flds <- createFolds(salary$Degree, k = 10, list = TRUE, returnTrain = FALSE)

K= c(1,3,5,7,9)

cv_error = matrix(NA, 5, 5)

for(j in 1:5){
  k = K[j]
  for(i in 1:5){
    test_index = flds[[i]]
    testX = standardized.X[test_index,]
    trainX = standardized.X[-test_index,]
    
    train.Y = salary$Degree[-test_index]
    test.Y = salary$Degree[test_index]
    
    knn.pred = knn(trainX,testX,train.Y,k=k)
    cv_error[i,j] = mean(test.Y!=knn.pred)
  }
}

knn_mc<-as.data.frame(cbind("K"=K, "MC" = colMeans(cv_error)))
plot(knn_mc$K, knn_mc$MC, xlab="K", ylab="Misclassification Rate", main="Misclassification Rate by K", type = "b")
```

```{r}
knn.pred = knn(trainX,testX,train.Y,k=1)
test.Y<-as.factor(test.Y)
levels(test.Y)<-c("P", "na", "M")
levels(knn.pred) = c("P", "na", "M")

conf_mat <- confusion_matrix(targets = test.Y, predictions = knn.pred)
plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]])
```
  

```{r}
salary1 <- read.csv(file = 'ds_salary_data2.csv')
region_key <- data.frame(state.abb, state.region)
salary1$state.abb <- as.factor(salary1$Job.Location)
salary<- merge(salary1,region_key, by = "state.abb")
salary<- salary[,-c(1,2,4,7,9,11,12)] 
salary$Size <- as.factor(salary$Size)
salary$Type.of.ownership<- as.factor(salary$Type.of.ownership)
salary$Sector <- as.factor(salary$Sector)
salary$Hourly <- as.factor(salary$Hourly)
salary$Python <- as.factor(salary$Python)
salary$excel <- as.factor(salary$excel)
salary$sql <- as.factor(salary$sql)
salary$sas <- as.factor(salary$sas)
salary$tableau <- as.factor(salary$tableau)
salary$job_title_sim <- as.factor(salary$job_title_sim)
salary$Degree <- as.factor(salary$Degree)
trimed = salary[!(salary$Degree == "na"),]
```

  
  
```{r}
#set.seed(1)
#n<-nrow(salary2)
#standardized.X = (salary2)%>%na.omit()

#flds <- createFolds(salary2$Degree, k = 10, list = TRUE, returnTrain = FALSE)

#K= c(1,3,5,7,9)

#cv_error = matrix(NA, 5, 5)

#for(j in 1:5){
#  k = K[j]
#  for(i in 1:5){
#    test_index = flds[[i]]
#    testX = standardized.X[test_index,]
#    trainX = standardized.X[-test_index,]
#    
#    train.Y = salary$Degree[-test_index]
#    test.Y = salary$Degree[test_index]
#    
#    knn.pred = knn(trainX,testX,train.Y,k=k)
#    cv_error[i,j] = mean(test.Y!=knn.pred)
#  }
#}

#knn_mc<-as.data.frame(cbind("K"=K, "MC" = colMeans(cv_error)))
#plot(knn_mc$K, knn_mc$MC, xlab="K", ylab="Misclassification Rate", main="Misclassification Rate by K", type = "b")
```
too many errors


```{r}
knn.pred = knn(trainX,testX,train.Y,k=1)
test.Y<-as.factor(test.Y)
levels(test.Y)<-c("P", "na", "M")
levels(knn.pred) = c("P", "na", "M")

conf_mat <- confusion_matrix(targets = test.Y, predictions = knn.pred)
plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]])
```


  
  
  